How Alignment Impact Language Learning Tasks? \\ A Visual Analytics Tool for Interpreting, Debugging, \\ and Tunning Text Entailment Model

### 2018-02-07 paper/paper_entailVis.tex
fix single prediction
init

%% Abstract section.
% What are we doing in this paper
\abstract{
(What is the highlevel motivation)
Making sense and explaining the predictions made by deep neural networks
is not only essential for validating and improving the model, but also
becoming a necessity with increasing requirement for model accountabilty (e.g., for medical
application), as well as ethics concerns regarding the potential harm the
hidden biases learned by a black-box model~\cite{}.
%

@@

(What did we bring)
Recently attention mechanism~\cite{} has gained a strong following in
the Natural Language Processs (NLP) research.

} % end of abstract

>>>>

%% Abstract section.
% What are we doing in this paper
\abstract{
(What is the highlevel motivation)
Making sense and explaining the predictions made by deep neural networks is not only essential for validating and improving the model, but also becoming a necessity with increasing requirement for model accountability (e.g., for medical application where the decision have serious consequences) and model fairness ( e.g., the model may capture and perpetuate the biases exists in the training data~\cite{}).

%

@@

(What did we bring)
Recently attention mechanism~\cite{} has gained a strong following in
the Natural Language Processs (NLP) research.
} % end of abstract
